---
title: "Import and save the South Carolina highway patrol stops"
author: "Corinne Riddell"
date: "January 1, 2019"
output: html_document
---

### Reproducibility note

The raw data was downloaded from the Stanford Policing Project's website. 
Because it is too large to host on GitHub, you will need to download the South 
Carolina .gz file. You can find South Carolina's data on this 
page: https://openpolicing.stanford.edu/data/. Then update the pathway on line 
19 to your pathway to the downloaded file if you want to reproduce the analysis 
from the very beginning. Otherwise, you can instead work with the intermediate data
products that we have included on GitHub. 

```{r load-libraries}
library(tidyverse)
library(lubridate)
```

```{r load_data_subset}
file_SC <- gzfile( "/Volumes/Untitled/Dropbox/Police-Stops/Raw-data/SC-clean.csv.gz" ) 

SC_subset <- read.csv( file_SC, 
                       stringsAsFactors = FALSE, 
                       header = T, 
                       nrows = 6000000 ) #pulls a 6-million-rows subset of the data

table( year(SC_subset$stop_date) ) #years 2005 to 2013
```

Restrict the subset to the years 2005 to 2012:

```{r restrict-years-2005-12}
SC_subset <- SC_subset %>% 
  filter( year(SC_subset$stop_date) %in% c(2005:2012) )
```

Usually we want to save the data as a .csv, but here we go against that best 
practice because the saved csv file would exceed 1 GB, which the Rdata file is 126 MB.

```{r save-enhanced-data}
#readr::write_csv(SC.sample, "../Data/Raw-data-05-12.csv")
save( SC_subset, file = "/Volumes/Untitled/Dropbox/Police-Stops/Raw-data/Raw-data-05-12.Rdata" )
```