---
title: "Add variables and conduct the exploratory data analysis"
author: "Corinne Riddell"
date: "Jan 2, 2019"
output: html_document
---

```{r load_libraries, echo=F, warning=F, message=F}
library(tidyverse)
library(lubridate)
```

```{r load-raw-data-subset}
# Update this pathway to where you saved these data in the previous Rmd file (0_Save-raw-date-subset.Rmd)
load(file = "/Volumes/Untitled/Dropbox/Police-Stops/Raw-data/Raw-data-05-12.Rdata") #loads SC_subset into the environment
```

```{r aggregate-to-daily-stops}
summary1 <- SC_subset %>% 
  group_by(stop_date) %>%
  summarise(visits_per_day = n())
```

There are heightened traffic stops on certain days of the year, mostly to check
for drunk or impaired driving. We refer to these days as "dangerous days". Such 
days often correspond to holidays. There are also heightened stops on weekends.

```{r add-variables-to-daily-and-aggregated-datasets}
SC_subset <- SC_subset %>%
  mutate(year = year(stop_date), 
         month = month(stop_date), 
         day = day(stop_date), 
         day_index = yday(stop_date), # day of the year
         day_of_week = weekdays(as.Date(stop_date)),
         fri_sat = ifelse(day_of_week %in% c("Friday", "Saturday"), 
                          "Friday or Saturday", "Another day"))
                    
summary1 <- summary1 %>% 
  arrange(stop_date) %>%
  mutate(year = year(stop_date), 
         month = month(stop_date), 
         day = day(stop_date), 
         day_counter = row_number(), # this is a bit hacky - would break if there was a day with zero visits
         day_index = yday(stop_date), # day of the year
         day_of_week = weekdays(as.Date(stop_date)),
         fri_sat = ifelse(day_of_week %in% c("Friday", "Saturday"), 
                          "Friday or Saturday", "Another day"))
                    
summary1 <- summary1 %>% mutate(
  dangerous_days = case_when(day == 31 & month == 12 ~ "New Year's",
                             day == 1 & month == 1 ~ "New Year's",
                             day == 4 & month == 7 ~ "Independence day",
                             day == 18 & month == 3 ~ "Day after St. Patrick's",
                             day %in% c(24, 25, 26) & month == 11 & year == 2005 ~ "Thanksgiving weekend", # Thanksgiving Thurs + Friday + Saturday
                             day %in% c(23, 24, 25) & month == 11 & year == 2006 ~ "Thanksgiving weekend",
                             day %in% c(22, 23, 24) & month == 11 & year == 2007 ~ "Thanksgiving weekend", 
                             day %in% c(28, 29, 30) & month == 11 & year == 2008 ~ "Thanksgiving weekend",
                             day %in% c(26, 27, 28) & month == 11 & year == 2009 ~ "Thanksgiving weekend", 
                             day %in% c(25, 26, 27) & month == 11 & year == 2010 ~ "Thanksgiving weekend",
                             day %in% c(24, 25, 26) & month == 11 & year == 2011 ~ "Thanksgiving weekend", 
                             day %in% c(22, 23, 24) & month == 11 & year == 2012 ~ "Thanksgiving weekend",
                             day %in% c(2,3,4,5) & month == 9 & year == 2005 ~ "Labor Day weekend", # Monday + preceding Friday, Saturday, Sunday
                             day %in% c(1,2,3,4) & month == 9 & year == 2006 ~ "Labor Day weekend",
                             day %in% c(1,2,3) & month == 9 & year == 2007 ~ "Labor Day weekend",
                             day == 31 & month == 8 & year == 2007 ~ "Labor Day weekend",
                             day == 1 & month == 9 & year == 2008 ~ "Labor Day weekend",
                             day %in% c(29, 30, 31) & month == 8 & year == 2008 ~ "Labor Day weekend",
                             day %in% c(4,5,6,7) & month == 9 & year == 2009 ~ "Labor Day weekend",
                             day %in% c(3,4,5,6) & month == 9 & year == 2010 ~ "Labor Day weekend",
                             day %in% c(2,3,4,5) & month == 9 & year == 2011 ~ "Labor Day weekend",
                             day %in% c(1,2,3) & month == 9 & year == 2012 ~ "Labor Day weekend",
                             day == 31 & month == 8 & year == 2012 ~ "Labor Day weekend")
)
```

The policy was implemented on December 9th, 2005.

```{r add-policy-indicator-to-aggregated-dataset}
summary1 <- summary1 %>%
  mutate(post_policy = case_when(year > 2005 ~ 1,
                                 year == 2005 & month < 12 ~ 0,
                                 year == 2005 & month == 12 & day >= 9 ~ 1,
                                 year == 2005 & month == 12 & day < 9 ~ 0))
```

Time trend of the number of stops per day, before and after the policy change.

Smoothed fitted lines are added separately for each year of data. 

Want to see whether there is a discontinuous change in the number of stops
between 2005 and 2006 (since the policy change is implemented in Dec 2005).

Want to also assess temporal patterns in the other years

```{r visualize-stops-per-day, echo = F, fig.width = 10, fig.height=5}
dim(SC_subset)
str(SC_subset)

ggplot(summary1, aes(x = as.Date(stop_date), y = visits_per_day)) + 
  geom_line(lwd = 0.25)+ 
  geom_point(aes(col = dangerous_days, pch = fri_sat)) + 
  scale_shape_manual(values = c(19,3)) +
  scale_color_discrete(na.value="black", 
                      breaks = c("New year's", "Day after St. Patrick's",
                                 "Independence day", "Labor Day weekend", 
                                 "Thanksgiving weekend")) +
  geom_vline(xintercept = as.numeric(as.Date("2005-12-09")), linetype=4, col = "red") +
  xlab("Date") + ylab("Number of traffic stops") + theme_minimal() +
  ggtitle("Number of stops over time") +
  guides(colour = guide_legend(title = element_blank()), shape = guide_legend(title = element_blank())) +
  geom_text(aes(x = as.Date("2005-12-09"), y = 4250), 
            label = "Primary seat belt\nenforcement began", col = "red",
            check_overlap = T, nudge_x = 75) + 
  geom_smooth(dat = summary1 %>% filter(post_policy == 0), aes(x = as.Date(stop_date), y = visits_per_day), span = 0.5) + 
  geom_smooth(dat = summary1 %>% filter(year == 2006), aes(x = as.Date(stop_date), y = visits_per_day), span = 0.5) +
  geom_smooth(dat = summary1 %>% filter(year == 2007), aes(x = as.Date(stop_date), y = visits_per_day), span = 0.5) +
  geom_smooth(dat = summary1 %>% filter(year == 2008), aes(x = as.Date(stop_date), y = visits_per_day), span = 0.5) +
  geom_smooth(dat = summary1 %>% filter(year == 2009), aes(x = as.Date(stop_date), y = visits_per_day), span = 0.5) +
  geom_smooth(dat = summary1 %>% filter(year == 2010), aes(x = as.Date(stop_date), y = visits_per_day), span = 0.5) +
  geom_smooth(dat = summary1 %>% filter(year == 2011), aes(x = as.Date(stop_date), y = visits_per_day), span = 0.5) +
  geom_smooth(dat = summary1 %>% filter(year == 2012), aes(x = as.Date(stop_date), y = visits_per_day), span = 0.5)

policy <- data.frame(year = c(2005:2006), Z = c(342,NA))  #this tiny data frame is used to draw a line in the following plots using geom_vline().

ggplot(summary1 %>% filter(year %in% c(2005, 2006)), aes(x = day_index, y = visits_per_day)) + 
  geom_point(aes(col = dangerous_days, pch = fri_sat)) + 
  geom_smooth(dat = summary1 %>% filter(post_policy == 0), aes(x = day_index, y = visits_per_day), span = 0.5) +  
  geom_smooth(dat = summary1 %>% filter(year == 2006), aes(x = day_index, y = visits_per_day), span = 0.5) +
  scale_color_discrete(na.value="black") +
  geom_vline(data = policy, aes(xintercept = Z), linetype = 4, col = "red") +
  xlab("Date") + ylab("Number of traffic stops") + theme_minimal() +
  ggtitle("Number of stops over time") + 
  facet_wrap(~ year, nrow = 2)

ggplot(summary1, aes(x = day_index, y = visits_per_day, group = year)) + 
  geom_point(aes(col = factor(year), pch = fri_sat)) + 
    geom_smooth(aes(col = factor(year)), span = 0.5) +
  scale_color_discrete(na.value="black") +
  geom_vline(data = policy, aes(xintercept = Z), linetype = 4, col = "red") +
  xlab("Date") + ylab("Number of traffic stops") + theme_minimal() +
  ggtitle("Number of stops over time") 

```

**Police department**

```{r print-police-dept}
table(SC_subset$police_department)

round(prop.table(table(SC_subset$police_department))*100, 2)

table(SC_subset$police_department, SC_subset$year)
```

Acronyms (from https://scdps.sc.gov/):

- BPS: Bureau of Protective Services. Note the fewer visits in 2005 vs other years
- IEU: Immigration enforcement unit: No visits in 2005/2006. Implemented in mid-2007
- SCHP: South Carolina Highway Patrol: This is the department of interext
- STP: State Transport Police: Charged with enforcement for commercial trucks/buses. Not of interest.

### Remake the above plots only using data from the highway patrol.

```{r inclue-highway-patrol-only}
summary2 <- SC_subset %>% 
  filter(police_department == "SCHP") %>%
  group_by(stop_date) %>%
  summarise(visits_per_day = n())
```

There are heightened traffic stops on certain days of the year, mostly to check
for drunk or impaired driving. We refer to these days as "dangerous days". Such 
days often correspond to holidays. There are also heightened stops on weekends.

```{r add-variables}
summary2 <- summary2 %>% 
  arrange(stop_date) %>%
  mutate(year = year(stop_date), 
         month = month(stop_date), 
         day = day(stop_date), 
         day_counter = row_number(), # this is a bit hacky - would break if there was a day with zero visits
         day_index = yday(stop_date), # day of the year
         day_of_week = weekdays(as.Date(stop_date)),
         fri_sat = ifelse(day_of_week %in% c("Friday", "Saturday"), 
                          "Friday or Saturday", "Another day")) %>% 
  mutate(
    dangerous_days = case_when(day == 31 & month == 12 ~ "New Year's",
                             day == 1 & month == 1 ~ "New Year's",
                             day == 4 & month == 7 ~ "Independence day",
                             day == 18 & month == 3 ~ "Day after St. Patrick's",
                             day %in% c(24, 25, 26) & month == 11 & year == 2005 ~ "Thanksgiving weekend", # Thanksgiving Thurs + Friday + Saturday
                             day %in% c(23, 24, 25) & month == 11 & year == 2006 ~ "Thanksgiving weekend",
                             day %in% c(22, 23, 24) & month == 11 & year == 2007 ~ "Thanksgiving weekend", 
                             day %in% c(28, 29, 30) & month == 11 & year == 2008 ~ "Thanksgiving weekend",
                             day %in% c(26, 27, 28) & month == 11 & year == 2009 ~ "Thanksgiving weekend", 
                             day %in% c(25, 26, 27) & month == 11 & year == 2010 ~ "Thanksgiving weekend",
                             day %in% c(24, 25, 26) & month == 11 & year == 2011 ~ "Thanksgiving weekend", 
                             day %in% c(22, 23, 24) & month == 11 & year == 2012 ~ "Thanksgiving weekend",
                             day %in% c(2,3,4,5) & month == 9 & year == 2005 ~ "Labor Day weekend", # Monday + preceding Friday, Saturday, Sunday
                             day %in% c(1,2,3,4) & month == 9 & year == 2006 ~ "Labor Day weekend",
                             day %in% c(1,2,3) & month == 9 & year == 2007 ~ "Labor Day weekend",
                             day == 31 & month == 8 & year == 2007 ~ "Labor Day weekend",
                             day == 1 & month == 9 & year == 2008 ~ "Labor Day weekend",
                             day %in% c(29, 30, 31) & month == 8 & year == 2008 ~ "Labor Day weekend",
                             day %in% c(4,5,6,7) & month == 9 & year == 2009 ~ "Labor Day weekend",
                             day %in% c(3,4,5,6) & month == 9 & year == 2010 ~ "Labor Day weekend",
                             day %in% c(2,3,4,5) & month == 9 & year == 2011 ~ "Labor Day weekend",
                             day %in% c(1,2,3) & month == 9 & year == 2012 ~ "Labor Day weekend",
                             day == 31 & month == 8 & year == 2012 ~ "Labor Day weekend")
) %>%
  mutate(post_policy = case_when(year > 2005 ~ 1,
                                 year == 2005 & month < 12 ~ 0,
                                 year == 2005 & month == 12 & day >= 9 ~ 1,
                                 year == 2005 & month == 12 & day < 9 ~ 0))
```

**Smoothed time trends in traffic stops for the highway patrol only, 2005-2012**

```{r}
ggplot(summary2, aes(x = day_index, y = visits_per_day, group = year)) + 
  #geom_point(aes(col = factor(year), pch = fri_sat)) + 
    geom_smooth(aes(col = factor(year)), span = 0.5, se = F) +
  scale_color_discrete(na.value="black") +
  geom_vline(data = policy, aes(xintercept = Z), linetype = 4, col = "red") +
  xlab("Date") + ylab("Number of traffic stops") + theme_minimal() +
  ggtitle("Number of stops over time") 
```

Can see that the largest difference among the years is between 2005 and 2006. 
The number of stops did continue to increase in 2007 and 2008, with 2009-2012 
overlapping more. 

**All variables (not yet described)**

```{r print-var-names}
names(SC_subset)
```

```{r restrict-to-2005-2006}
SC_05_06 <- SC_subset %>% 
  mutate(year = year(stop_date)) %>% 
  filter(year %in% c(2005, 2006))
```

Examine variable values:

**Counties**

```{r print-county-names}
length(unique(SC_05_06$county_name))
unique(SC_05_06$county_name)

round( prop.table( table( SC_05_06$county_name == "" ) ) * 100, 1 )
```

**Gender, age, race**

```{r drive-demographics} 
table(SC_05_06$driver_gender, useNA = "always")
round(prop.table(table(SC_05_06$driver_gender, useNA = "always")) * 100, 1)

#raw race and race re-code
table(SC_05_06$driver_race_raw)
table(SC_05_06$driver_race, SC_05_06$driver_race_raw)

round(prop.table(table(SC_05_06$driver_race, useNA = "always"))*100,1)

ggplot(SC_05_06 %>% filter(driver_race %in% c("Black", "Hispanic", "White")), aes(driver_age)) + 
  geom_histogram(col = "white", binwidth = 5, fill = "#15534C") + 
  facet_wrap( ~ driver_race) + 
  ggtitle("Histogram of driver's age for blacks, whites, and Hispanics") +
  theme_minimal() + labs(x = "Age", y = "Count")

ggplot(SC_05_06 %>% filter(driver_race %in% c("Black", "Hispanic", "White")), aes(driver_age)) + 
  geom_density(col = "white", aes(fill = driver_race), alpha = 0.5) + 
  ggtitle("Histogram of driver's age for blacks, whites, and Hispanics") +
  theme_minimal() + labs(x = "Age", y = "Count")

#include only highway patrol stops
ggplot(SC_05_06 %>% filter(driver_race %in% c("Black", "Hispanic", "White"), police_department == 'SCHP'), aes(driver_age)) + 
  geom_density(col = "white", aes(fill = driver_race), alpha = 0.5) + 
  ggtitle("Histogram of driver's age for blacks, whites, and Hispanics") +
  theme_minimal() + labs(x = "Age", y = "Count")

#stratify by gender
ggplot(SC_05_06 %>% filter(driver_race %in% c("Black", "Hispanic", "White")), aes(driver_age)) + 
  geom_density(col = "white", aes(fill = driver_race), alpha = 0.5) + 
  ggtitle("Histogram of driver's age for blacks, whites, and Hispanics") +
  theme_minimal() + labs(x = "Age", y = "Count") +
  facet_wrap(~driver_gender)
```

Note: Hispanic drivers are younger that White and Black drivers. Much fewer of them
are older than 50. 

**Violation**

```{r violation-informaiton}
length(unique(SC_05_06$violation_raw))
table(SC_05_06$violation_raw, SC_05_06$police_department, useNA = "always")

length(unique(SC_05_06$violation))
table(SC_05_06$violation, useNA = "always")

```

Can see that the BPS and STP have relatively more stops for excess weight, length,
or width and other commercial-truck related violations.

**Stop purpose**

```{r stop-purpose}
table(SC_05_06$stop_purpose, useNA = "always")
round(prop.table(table(SC_05_06$stop_purpose, useNA = "always"))*100, 1)
round(prop.table(table(SC_05_06$driver_race, SC_05_06$stop_purpose), 1)*100, 1)

table(SC_05_06$stop_purpose, SC_05_06$police_department, useNA = "always")
table(SC_subset$stop_purpose, SC_subset$police_department, useNA = "always")
```

**Search and contraband**

```{r search-contraband}
SC_05_06 %>% count(search_conducted)

table(SC_05_06$search_conducted)
round(prop.table(table(SC_05_06$search_conducted))*100,1)

table(SC_05_06$search_type_raw)

table(SC_05_06$contraband_found)

round(prop.table(table(SC_05_06$search_conducted, SC_05_06$contraband_found), 1)*100, 1)
```

**Stop outcome**

```{r stop-outcome}
table(SC_05_06$stop_outcome)
round(prop.table(table(SC_05_06$stop_outcome))*100, 1)

table(SC_05_06$driver_race, SC_05_06$stop_outcome)
round(prop.table(table(SC_05_06$driver_race, SC_05_06$stop_outcome), 1)*100, 1)

table(SC_05_06$is_arrested)
round(prop.table(table(SC_05_06$is_arrested))*100, 1)
round(prop.table(table(SC_05_06$driver_race, SC_05_06$is_arrested), 1)*100, 1)
```

**Officer id, race, age**

```{r office-demographics}
officer_level <- SC_05_06 %>% 
  group_by(officer_id, year) %>%
  summarise(num_stops_per_officer_year = n()) 

ggplot(officer_level %>% filter(officer_id != "", year == 2005), 
       aes(x = num_stops_per_officer_year)) + 
  geom_histogram(binwidth = 25, col = "white")

SC_05_06 %>% 
  group_by(year(stop_date)) %>% 
  summarise(num_officers = length(unique(officer_id)),
            ave_num_stops = round(n()/num_officers))

officer_ids_2005 <- SC_05_06 %>%
  filter(year(stop_date) == 2005) %>% 
  select(officer_id) %>% unique()

officer_ids_2006 <- SC_05_06 %>%
  filter(year(stop_date) == 2006) %>% 
  select(officer_id) %>% unique()

officer_ids_bothyears <- inner_join(officer_ids_2005, officer_ids_2006)

SC_05_06 %>% filter(officer_id %in% officer_ids_bothyears$officer_id) %>% dim()

table(SC_05_06$officer_race)
round(prop.table(table(SC_05_06$officer_race)) * 100, 2)

ggplot(SC_05_06 %>% 
         filter(officer_race %in% c("Black", "White")), aes(officer_age)) + 
  geom_histogram(binwidth = 5, col = "white", fill = "#15534C") + 
  ggtitle("Histogram of officers's age for black and white officers") + 
  facet_wrap(~ officer_race)+
  theme_minimal() + xlab("Age") + ylab("Count")
```

**Example county**

```{r example-county}
Abbeville <- SC_05_06 %>% filter(county_name == "Abbeville County")
Abbeville %>% group_by(road_number) %>% tally() %>% arrange(-n)
```

```{r save-enhanced-data}
save(summary1, file = "../Data/Aggregated-data-05-12.Rdata")
save(SC_05_06, file = "../Data/Enhanced-data-05-06.Rdata")
```
